---
title: "4198 Final Min Yang"
output:
  word_document: default
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
data <- read.csv(file = "~/Desktop/fordTrain.csv",
stringsAsFactors=TRUE)

indexes <- read.csv(file = "~/Desktop/indexes.csv",
header=FALSE,
stringsAsFactors=TRUE)


last.two.digits<- 31
k<-last.two.digits+1

newdata<-data.frame(data[data[,1]%in%indexes[k,], ])
summary(newdata)
```

#Exploratory Data Analysis
##1. Remove features which do not change their values
```{r}
remove<-c("P8","V7","V9") #remove perfect relationship
newdata1<-newdata[,!(names(newdata) %in% remove)]
```
##2. specify  
```{r}
str(newdata1)
```

```{r}
n =dim(newdata)[1]
m =dim(newdata)[2]
par(mfrow=c(3,2))
for(i in 1:m)
  {
  if(is.numeric(newdata[,i])) 
  hist(newdata[,i],xlab=names(newdata)[i]) else 
  barplot(table(newdata[,i]),xlab=names(newdata)[i])
  }
```

```{r}
E3<-as.factor(newdata$E3)
levels(E3)
E7<-as.factor(newdata$E7)
levels(E7)
E8<-as.factor(newdata$E8)
levels(E8)
E9<-as.factor(newdata$E9)
levels(E9)
V3<-as.factor(newdata$V3)
levels(V3)
V5<-as.factor(newdata$V5)
levels(V5)
V10<-as.factor(newdata$V10)
levels(V10)
```
```{r}
n_occur <- data.frame(table(newdata$P1))
n_occur[n_occur$Freq > 1,]

```


##3.investigate feature relationship
```{r}
library(ggplot2)
library(gridExtra)
```
```{r}
p1a<-ggplot(newdata,aes(x=P1,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
p1b<-ggplot(newdata,aes(x=P1,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(p1a, p1b, ncol=2)
```

```{r}
p2a<-ggplot(newdata,aes(x=P2,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
p2b<-ggplot(newdata,aes(x=P2,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(p2a, p2b, ncol=2)
```
```{r}
p3a<-ggplot(newdata,aes(x=P3,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
p3b<-ggplot(newdata,aes(x=P3,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(p3a, p3b, ncol=2)
```

```{r}
p4a<-ggplot(newdata,aes(x=P4,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
p4b<-ggplot(newdata,aes(x=P4,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(p4a, p4b, ncol=2)
```

```{r}
p5a<-ggplot(newdata,aes(x=P5,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
p5b<-ggplot(newdata,aes(x=P5,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(p5a, p5b, ncol=2)
```
```{r}
p6a<-ggplot(newdata,aes(x=P6,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
p6b<-ggplot(newdata,aes(x=P6,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(p6a, p6b, ncol=2)
```
```{r}
p7a<-ggplot(newdata,aes(x=P7,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
p7b<-ggplot(newdata,aes(x=P7,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(p7a, p7b, ncol=2)
```
```{r}
e1a<-ggplot(newdata,aes(x=E1,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e1b<-ggplot(newdata,aes(x=E1,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e1a, e1b, ncol=2)
```
```{r}
e2a<-ggplot(newdata,aes(x=E2,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e2b<-ggplot(newdata,aes(x=E2,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e2a, e2b, ncol=2)
```
```{r}
e3a<-ggplot(newdata,aes(x=E3,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e3b<-ggplot(newdata,aes(x=E3,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e3a, e3b, ncol=2)
```
```{r}
e4a<-ggplot(newdata,aes(x=E4,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e4b<-ggplot(newdata,aes(x=E4,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e4a, e4b, ncol=2)
```
```{r}
e5a<-ggplot(newdata,aes(x=E5,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e5b<-ggplot(newdata,aes(x=E5,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e5a, e5b, ncol=2)
```
```{r}
e6a<-ggplot(newdata,aes(x=E6,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e6b<-ggplot(newdata,aes(x=E6,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e6a, e6b, ncol=2)
```
```{r}
e7a<-ggplot(newdata,aes(x=E7,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e7b<-ggplot(newdata,aes(x=E7,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e7a, e7b, ncol=2)
```

```{r}
e8a<-ggplot(newdata,aes(x=E8,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e8b<-ggplot(newdata,aes(x=E8,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e8a, e8b, ncol=2)
```

```{r}
e9a<-ggplot(newdata,aes(x=E9,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e9b<-ggplot(newdata,aes(x=E9,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e9a, e9b, ncol=2)
```
```{r}
e10a<-ggplot(newdata,aes(x=E10,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e10b<-ggplot(newdata,aes(x=E10,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e10a, e10b, ncol=2)
```
```{r}
e11a<-ggplot(newdata,aes(x=E11,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
e11b<-ggplot(newdata,aes(x=E11,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(e11a, e11b, ncol=2)
```

```{r}
v1a<-ggplot(newdata,aes(x=V1,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v1b<-ggplot(newdata,aes(x=V1,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v1a, v1b, ncol=2)
```
```{r}
v2a<-ggplot(newdata,aes(x=V2,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v2b<-ggplot(newdata,aes(x=V2,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v2a, v2b, ncol=2)
```
```{r}
v3a<-ggplot(newdata,aes(x=V3,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v3b<-ggplot(newdata,aes(x=V3,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v3a, v3b, ncol=2)
```

```{r}
v4a<-ggplot(newdata,aes(x=V4,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v4b<-ggplot(newdata,aes(x=V4,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v4a, v4b, ncol=2)
```
```{r}
v5a<-ggplot(newdata,aes(x=V5,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v5b<-ggplot(newdata,aes(x=V5,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v5a, v5b, ncol=2)
```

```{r}
v6a<-ggplot(newdata,aes(x=V6,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v6b<-ggplot(newdata,aes(x=V6,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v6a, v6b, ncol=2)
```
```{r}
v8a<-ggplot(newdata,aes(x=V8,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v8b<-ggplot(newdata,aes(x=V8,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v8a, v8b, ncol=2)
```
```{r}
v10a<-ggplot(newdata,aes(x=V10,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v10b<-ggplot(newdata,aes(x=V10,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v10a, v10b, ncol=2)
```
```{r}
v11a<-ggplot(newdata,aes(x=V11,group=IsAlert,fill=IsAlert))+  geom_histogram(position="dodge",binwidth=70)+theme_bw()
v11b<-ggplot(newdata,aes(x=V11,group=IsAlert,fill=IsAlert))+  geom_histogram(position="fill",binwidth=70)+theme_bw()
grid.arrange(v11a, v11b, ncol=2)
```

##4. identify paris of features which are relathed to each other
```{r}
pairs(newdata1[,c(3,4,5,6,7,8,9,10)])
```
```{r}
pairs(newdata1[,c(3,11,12,13,14,15,16,17,18,19,20,21)])
```
```{r}
pairs(newdata1[,c(3,22,23,24,25,26,27,28,29,30)])
```

##5. dimension reduction 
###a)
```{r}
remove<-c("P2","P5","E5","V2","V11") #remove no relationship
newdata2<-newdata1[,!(names(newdata1) %in% remove)]
```
###b)
```{r}
plot(newdata2$V1,newdata2$V4)
```
```{r}
plot(newdata2$P3,newdata2$P4)
```

```{r}
remove1<-c("P4","V4") #remove perfect relationship and non linear relationship
newdata3<-newdata2[,!(names(newdata2) %in% remove1)]
```
```{r}
newdata3$P6<-log(as.numeric(newdata3$P6)) #transformation
```
```{r}
summary(newdata3$V3)
```
```{r}
binned.V3 <-1*(newdata3$V3<255)+2*(newdata3$V3<511)*(newdata3$V3>254)+3*(newdata3$V3<767)*(newdata3$V3>510)+4*(newdata3$V3>766)
newdata3$V3 <-factor(binned.V3,label=c("level1","level2","level3","level4"))
table(newdata3$V3)
```

#Basic Model Building
##neural network
```{r}
newdat<-newdata3
#Check indicator variables
unique(newdat$E3)
unique(newdat$E7)
unique(newdat$E8)
unique(newdat$E9)
unique(newdat$V3)
unique(newdat$V5)
unique(newdat$V10)
```
```{r}
newdat$E3_1 = c(rep(0, length(newdat$IsAlert)))
newdat$E3_0 = c(rep(0, length(newdat$IsAlert)))
newdat$E3_4 = c(rep(0, length(newdat$IsAlert)))
newdat$E7_low = c(rep(0, length(newdat$IsAlert)))
newdat$E7_high = c(rep(0, length(newdat$IsAlert)))
newdat$E8_low = c(rep(0, length(newdat$IsAlert)))
newdat$E8_high = c(rep(0, length(newdat$IsAlert)))
newdat$E9_0 = c(rep(0, length(newdat$IsAlert)))
newdat$E9_1 = c(rep(0, length(newdat$IsAlert)))
newdat$V3_1 = c(rep(0, length(newdat$IsAlert)))
newdat$V3_2  = c(rep(0, length(newdat$IsAlert)))
newdat$V3_3 = c(rep(0, length(newdat$IsAlert)))
newdat$V3_4= c(rep(0, length(newdat$IsAlert)))
newdat$V5_0 = c(rep(0, length(newdat$IsAlert)))
newdat$V5_1 =c(rep(0, length(newdat$IsAlert))) 
newdat$V10_low = c(rep(0, length(newdat$IsAlert)))
newdat$V10_high = c(rep(0, length(newdat$IsAlert)))
```

```{r}
#Create dummy variable
for (i in 1:length(newdata$IsAlert)) {
#E3
if(newdat$E3[i] == 1) newdat$E3_1[i] <- 1 
if(newdat$E3[i] == 0) newdat$E3_0[i] <- 1 
if(newdat$E3[i] == 4) newdat$E3_4[i] <- 1
#E7
if(newdat$E7[i] <= 10) newdat$E7_low[i] <- 1 
if(newdat$E7[i] > 10) newdat$E7_high[i] <- 1
#E8
if(newdat$E8[i] <= 4) newdat$E8_low[i] <- 1 
if(newdat$E8[i] > 4) newdat$E8_high[i] <- 1
#E9
if(newdat$E9[i] == 1) newdat$E9_1[i] <- 1 
if(newdat$E9[i] == 0) newdat$E9_0[i] <- 1
#V3
if(newdat$V3[i] == "level1") newdat$V3_1[i] <- 1 
if(newdat$V3[i] == "level2") newdat$V3_2[i] <- 1
if(newdat$V3[i] == "level3") newdat$V3_3[i] <- 1 
if(newdat$V3[i] == "level4") newdat$V3_4[i] <- 1
#V5
if(newdat$V5[i] == 1) newdat$V5_1[i] <- 1 
if(newdat$V5[i] == 0) newdat$V5_0[i] <- 1
#V10
if(newdat$V10[i] <= 3) newdat$V10_low[i] <- 1
if(newdat$V10[i] > 3) newdat$V10_high[i]<- 1 }
```


```{r}
# Minimax transform the continuous variables
#P1
newdat$P1_mm <-(newdat$P1-min(newdat$P1))/(max(newdat$P1)-min(newdat$P1))
#P3
newdat$P3_mm <- (newdat$P3 - min(newdat$P3)) / (max(newdat$P3) - min(newdat$P3))
#P6
newdat$P6_mm <- (newdat$P6 - min(newdat$P6)) / (max(newdat$P6) - min(newdat$P6))
#P7
newdat$P7_mm <- (newdat$P7 - min(newdat$P7)) / (max(newdat$P7) - min(newdat$P7))
#E1
newdat$E1_mm <- (newdat$E1 - min(newdat$E1)) / (max(newdat$E1) - min(newdat$E1))
#E2
newdat$E2_mm  <- (newdat$E2 - min(newdat$E2)) / (max(newdat$E2) - min(newdat$E2))
#E4
newdat$E4_mm  <- (newdat$E4 - min(newdat$E4)) / (max(newdat$E4) - min(newdat$E4))
#E6
newdat$E6_mm  <- (newdat$E6 - min(newdat$E6)) / (max(newdat$E6) - min(newdat$E6))
#E10
newdat$E10_mm <- (newdat$E10 - min(newdat$E10)) / (max(newdat$E10) - min(newdat$E10))
#E11
newdat$E11_mm  <- (newdat$E11 - min(newdat$E11)) / (max(newdat$E11) - min(newdat$E11))
#V1
newdat$V1_mm  <- (newdat$V1 - min(newdat$V1)) / (max(newdat$V1) - min(newdat$V1))
#V6
newdat$V6_mm  <- (newdat$V6 - min(newdat$V6)) / (max(newdat$V6) - min(newdat$V6))
#V8
newdat$V8_mm  <- (newdat$V8 - min(newdat$V8)) / (max(newdat$V8) - min(newdat$V8))

```

```{r}
#new dataset
nndata <- newdat[ , -c(4:23)]
nndata <- nndata[, -c(1, 2)] 
```


```{r}
library(caret)
#training data 
index <- createDataPartition(nndata$IsAlert, p=0.75, list=FALSE)
nntrain <-nndata[index,] #75%
nntest <-nndata[-index,]  #25%
```
##Neural Network
```{r}
library(nnet)
```
```{r}
set.seed(1)
myNewFrame <- data.frame(node = integer(0),maxit = integer(0), decay = integer(0) ,misscls.train = integer(0), misscls.test = integer(0))

for (m in c(500, 1000)) {
  for (d in c(0, 0.2, 0.5)) {
    for (s in c(5,10,15)){
    net.dat <- nnet(IsAlert~.,type='class', data = nntrain, size = s, decay = d, maxit = m)
    #table(round(net.dat$fitted.values, 1))
    estimated_IsAlert=as.numeric(net.dat$fitted.values>0.5)
    T = table(estimated_IsAlert,nntrain$IsAlert)
    misscls.train<-sum((estimated_IsAlert-nntrain$IsAlert)^2)/length(nntrain$IsAlert)
    misscls.train
    presdicted.testing<-as.numeric(predict(net.dat,nntest )>0.5)
    Ttest = table(presdicted.testing, nntest$IsAlert)
    misscls.test<-sum((presdicted.testing-nntest$IsAlert)^2)/length(nntest$IsAlert)
    misscls.test
  
    df <- data.frame(s, m, d, misscls.train, misscls.test)
    names(df)<-c("node", "maxit", "decay", "misscls.train", "misscls.test")
    myNewFrame <- rbind(myNewFrame, df)
  }
  }
}
myNewFrame
```


```{r}
library(pROC)
mod1 <- nnet(IsAlert~.,type='class', data = nntrain, size = 10, decay = 0.2, maxit = 1000)
nnet1.predict.train<-predict(mod1,nntrain )
roc.nnet1<-roc(nntrain[,1], as.numeric(nnet1.predict.train))
plot(roc.nnet1)
auc.score.nnet1<-auc(nntrain[,1], as.numeric(nnet1.predict.train))
auc.score.nnet1

nnet1.predict.test<-predict(mod1,nntest )
roc.nnet1<-roc(nntest[,1], as.numeric(nnet1.predict.test))
plot(roc.nnet1)
auc.score.nnet1<-auc(nntest[,1],as.numeric( nnet1.predict.test))
auc.score.nnet1
```

##logistic regression

```{r}
library(caret)
#new data set
lmdata <- newdat[ , -c(41:53)]
lmdata <- lmdata[ , -c(1:2)]
#training data 
index <- createDataPartition(lmdata$IsAlert, p=0.75, list=FALSE)
trainSet <-lmdata[index,] #75%
testSet <-lmdata[-index,]  #25%
```
```{r}
str(lmdata)
```

```{r}
glm1<-glm(IsAlert~.,data=trainSet,family="binomial")
glm1.predict.test<-predict(glm1,testSet,type="response")
summary(glm1)
```

```{r}
glm2 <- glm(IsAlert~P3+ P6 + P7 + E1+ E2+ E6+ E10+ E11 + V1+V6+V8, data = trainSet, family="binomial") 
summary(glm2)
```

```{r}
glm3 <- glm(IsAlert ~P3+P6+P7+E1+E2+E6+E10+E11+V1+V8 , data = trainSet, family="binomial") 
summary(glm3)
```

```{r}
library(pROC)
glm3.predict.train<-predict(glm3,trainSet,type="response")
roc.glm<-roc(trainSet$IsAlert, glm3.predict.train)
plot(roc.glm)
auc.score.glm<-auc(trainSet$IsAlert, glm3.predict.train)
auc.score.glm

glm3.predict.test<-predict(glm3,testSet,type="response")
roc.glm2<-roc(testSet$IsAlert, glm3.predict.test)
plot(roc.glm2)
auc.score.glm2<-auc(testSet$IsAlert, glm3.predict.test)
auc.score.glm2
```

##Desion Tree

```{r}
library(caret)
datatree <-newdata3[,3:23]
#training data 
index <- createDataPartition(datatree$IsAlert, p=0.75, list=FALSE)
training <-datatree[index,] #75%
testing <-datatree[-index,]  #25%
summary(training)

```
```{r}
IsAlert=ifelse(datatree$IsAlert == 1," yes"," No ") 
datatree <- data.frame(datatree[,-1],IsAlert) 
summary(datatree)
```

```{r}
library(tree)
tree.fit =tree(IsAlert~.,data=datatree )
summary (tree.fit )
```

```{r}
plot(tree.fit)
text(tree.fit, pretty=0)
tree.fit
```

```{r}
set.seed(2)
testing$IsAlert <- as.factor(testing$IsAlert)
tree.pred <- predict(tree.fit, testing, type="class")
tree.table <- table(tree.pred, testing$IsAlert)
tree.pred.prob<-predict(tree.fit, testing)
library(pROC)
roc.curve <- roc( as.numeric(testing$IsAlert),
tree.pred.prob[,2])
plot(roc.curve, main = "ROC: Classification Tree", col = "red")
auc.score<-auc(as.numeric(testing$IsAlert),tree.pred.prob[,2])
auc.score
tree.pred1.prob<-predict(tree.fit, training)
auc.score2<-auc(as.numeric(training$IsAlert),tree.pred1.prob[,2])
auc.score2
```

#application of learning techniques
##boosting for tree
```{r}
library(randomForest)
bagging =randomForest(as.factor(IsAlert)~.,data=training , mtry=4, ntree =100,importance=TRUE)
tree.pred = predict ( bagging ,newdata =testing,type="prob") 
summary(tree.pred)
```
```{r}
library(pROC)
tree.train = predict ( bagging ,newdata =training,type="prob") 
roc.tree1<-roc(training$IsAlert, tree.train[,2])
plot(roc.tree1)
auc.score.bagged<-auc(training$IsAlert, tree.train[,2])
auc.score.bagged

roc.tree<-roc(testing$IsAlert, tree.pred[,2])
plot(roc.tree)
auc.score.bagged<-auc(testing$IsAlert, tree.pred[,2])
auc.score.bagged
```


#Ensemble
```{r}
library(caret)
set.seed(1)
sum(is.na(newdata))
```

```{r}
#Defining the training controls for multiple models
fitControl <- trainControl(
  method = "cv",
  number = 5,
savePredictions = 'final',
classProbs = T)

#Defining the predictors and outcome
predictors<-c("P3","P6","P7","E1", "E2", "E6", "E10", "E11", "V1", "V8")
outcomeName<-'IsAlert'

```


```{r}
#Training the random forest model
model_rf<-train(trainSet[,predictors],ifelse(trainSet[,1]=="1","YES","NO"),
method='rf',tuneGrid = data.frame(mtry = 10),ntree=1,
trControl=fitControl,tuneLength=1)
```

```{r}
#Predicting using random forest model
testSet$pred_rf<-predict(object = model_rf,testSet[,predictors])
```
```{r}
#Checking the accuracy of the random forest model
table(testSet$IsAlert,testSet$pred_rf)
```
```{r}
(6096+8988)/(6096+8988+160+160)
```

accurancy=0.98

```{r}
#Training the logistic regression model
model_lr<-train(trainSet[,predictors],ifelse(trainSet[,1]=="1","YES","NO"),
method='glm',trControl=fitControl,tuneLength=3)

```

```{r}
#Predicting using logistic regression model
testSet$pred_lr<-predict(object = model_lr,testSet[,predictors])

#Checking the accuracy of the logistic regression model
table(testSet$IsAlert,testSet$pred_lr)
```
```{r}
(5029+7798)/(1350+1227+5029+7798)
```

accurancy=0.83

```{r}

#Predicting the out of fold prediction probabilities for training data
trainSet$OOF_pred_rf<-model_rf$pred$Y[order(model_rf$pred$rowIndex)]
trainSet$OOF_pred_lr<-model_lr$pred$Y[order(model_lr$pred$rowIndex)]

#Predicting probabilities for the test data
testSet$OOF_pred_rf<-predict(model_rf,testSet[,predictors],type='prob')$Y
testSet$OOF_pred_lr<-predict(model_lr,testSet[,predictors],type='prob')$Y

#Predictors for top layer models 
predictors_top<-c('OOF_pred_rf','OOF_pred_lr') 

#GBM as top layer model 
model_gbm<- train(trainSet[,predictors_top],trainSet[,outcomeName],method='gbm',trControl=fitControl,tuneLength=3)

#predict using GBM top layer model
testSet$gbm_stacked<-predict(model_gbm,testSet[,predictors_top])

#Logistic regression as top layer model
model_glm<-train(trainSet[,predictors_top],trainSet[,outcomeName],method='glm',trControl=fitControl,tuneLength=3)

#predict using logictic regression top layer model
testSet$glm_stacked<-predict(model_glm,testSet[,predictors_top])
```

```{r}
library(pROC)

trainSet$gbm_stacked<-predict(model_gbm,trainSet[,predictors_top])
roc.gbmf<-roc(trainSet$IsAlert, trainSet$gbm_stacked)
plot(roc.gbmf)
auc.score.gbmf<-auc(trainSet$IsAlert, trainSet$gbm_stacked)
auc.score.gbmf

testSet$gbm_stacked<-predict(model_gbm,testSet[,predictors_top])
roc.gbmf<-roc(testSet$IsAlert, testSet$gbm_stacked)
plot(roc.gbmf)
auc.score.gbmf<-auc(testSet$IsAlert, testSet$gbm_stacked)
auc.score.gbmf

```
```{r}
trainSet$glm_stacked<-predict(model_glm,trainSet[,predictors_top])

roc.glmf<-roc(trainSet$IsAlert, trainSet$glm_stacked)
plot(roc.glmf)
auc.score.glmf<-auc(trainSet$IsAlert, trainSet$glm_stacked)
auc.score.glmf

roc.glmf<-roc(testSet$IsAlert, testSet$glm_stacked)
plot(roc.glmf)
auc.score.glmf<-auc(testSet$IsAlert, testSet$glm_stacked)
auc.score.glmf
```



